\documentclass[12 pt, a4paper]{article}
\usepackage[margin=0.35 in, top = 1 in , bottom = 1 in]{geometry}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{enumerate}
\pagestyle{fancy}
\linespread{1}
\begin{document}
\begin{Form}
\lhead{CICU College Profile}
\rhead{Due: August 1}
\begin{enumerate}\item Please use the space below to provide a summary description of your institution for prospective students/families (approximately 375 words or less). [7] \medskip

\underline{Previous Answer}: Founded in 1870, St. John's University is a Catholic and Vincentian university that prepares students for ethical leadership in today's global society. St John's has four campuses - Queens, Staten Island, and Manhattan in New York and Rome Italy. The University also has three academic locations - Hauppauge, New York; Paris, France; and Limerick, Ireland. Students come to St. John's from 47 states and 123 countries. \\

The University offers more than 100 associate, bachelor's, master's, and doctoral degree programs in the arts, business, education, law, pharmacy, and the natural and applied sciences. Students benefit from academic service learning activities, extensive global studies opportunities, an alumni network of over 184000 and 17 NCAA, Division I men's and women's athletic teams. New students have the option to receive laptops and all students have access to St. John's award-winning wireless network.\medskip

\TextField[width = 6 in,multiline, name=90010]{} \medskip

\item Please use the space below to provide unique attributes and additional or miscellaneous information about your institution.  For example, if your institution has branch campuses please list campus names, addresses, and admission office telephone numbers here.  In addition, please specify other attributes such as women-only campus, transfer-only campus, etc. [8] \medskip

\underline{Previous Answer}: Staten Island Campus: 300 Howard Avenue, Staten Island NY 10301, (718) - 390 - 4500. \\
Manhattan Campus: 101 Astor Place New York NY 10003, (718)-990-2000\medskip

\TextField[width = 6 in,multiline, name=90011]{} \medskip

\end{enumerate}
\newpage
\end{Form}
\end{document}
