\documentclass[12 pt, a4paper]{article}
\usepackage[margin=0.35 in, top = 1 in , bottom = 1 in]{geometry}
\usepackage{multicol}
\usepackage{hyperref}
\usepackage{fancyhdr}
\usepackage{enumerate}
\pagestyle{fancy}
\linespread{1}
\begin{document}
\begin{Form}
\lhead{CICU College Profile}
\rhead{Due: August 1}
\begin{enumerate}\item Primary Contact Information: Name [1a] \medskip

\underline{Previous Answer}: Adam Constantine\medskip

\TextField[width = 6 in,multiline, name=90000]{} \medskip

\item Primary Contact Information: Institution Name [1c] \medskip

\underline{Previous Answer}: St. John's University\medskip

\TextField[width = 6 in,multiline, name=90001]{} \medskip

\item Primary Contact Information: Title [1d] \medskip

\underline{Previous Answer}: Asscociate Director of Institutional Research\medskip

\TextField[width = 6 in,multiline, name=90002]{} \medskip

\item Primary Contact Information: Email [1e] \medskip

\underline{Previous Answer}: constana@stjohns.edu\medskip

\TextField[width = 6 in,multiline, name=90003]{} \medskip

\item Primary Contact Information: Telephone (include area code) [1f] \medskip

\underline{Previous Answer}: 7189906998\medskip

\TextField[width = 6 in,multiline, name=90004]{} \medskip

\item Does your institution provide virtual campus tours via its website? [2] \medskip

\underline{Choices}: Yes; No\medskip

\underline{Previous Answer}: Yes\medskip

\TextField[width = 6 in,multiline, name=90005]{} \medskip

\item Please provide a link to information about virtual campus tours. [3] \medskip

\underline{Previous Answer}: https://www.stjohns.edu/about/campuses-and-locations/queens-campus/explore-queens-campus\medskip

\TextField[width = 6 in,multiline, name=90006]{} \medskip

\item Please provide a link to information about campus visits. [4] \medskip

\underline{Previous Answer}: https://www.stjohns.edu/about/campuses-and-locations/queens-campus\medskip

\TextField[width = 6 in,multiline, name=90007]{} \medskip

\item Please provide a link to your admissions application. [5] \medskip

\underline{Previous Answer}: https://apply.stjohns.edu/apply/\medskip

\TextField[width = 6 in,multiline, name=90008]{} \medskip

\item Please provide a link to your institution's most recent class profile. [6] \medskip

\TextField[width = 6 in,multiline, name=90009]{} \medskip

\item How would you describe your institution's enrollment? [9] \medskip

\underline{Choices}: Undergraduate only; Graduate/first professional only; Both undergraduate and graduate/first professional\medskip

\underline{Previous Answer}: Both undergraduate and graduate / first professional\medskip

\TextField[width = 6 in,multiline, name=90012]{} \medskip

\item Please indicate the in-state tuition amount of typical full-time undergraduate students for the full academic year. Report an average tuition that includes all students at all levels (freshmen, sophomores, etc.). [12] \medskip

\underline{Previous Answer}: 41900\medskip

\TextField[width = 6 in,multiline, name=90015]{} \medskip

\item Please indicate the required fees amount (in-state) for typical full-time undergraduate students for the full academic year. [13] \medskip

\underline{Previous Answer}: 830\medskip

\TextField[width = 6 in,multiline, name=90016]{} \medskip

\item Please indicate the per credit hour charge for part-time undergraduate students for the full academic year. Please report an average per credit hour charge that includes all students at all levels (freshmen, sophomores, etc.). [14] \medskip

\underline{Previous Answer}: 1397\medskip

\TextField[width = 6 in,multiline, name=90017]{} \medskip

\item Please record any comments or additional stipulations on undergraduate tuition and fees. [15] \medskip

\underline{Previous Answer}: Tuition and fees may vary by program, class year, campus/location, meal plan and room type. Freshman have an additional new fee of 250\medskip

\TextField[width = 6 in,multiline, name=90018]{} \medskip

\item Does your institution offer room or board (meal plan) to undergraduate students? [16] \medskip

\underline{Choices}: Yes; No \medskip

\underline{Previous Answer}: Yes\medskip

\TextField[width = 6 in,multiline, name=90019]{} \medskip

\item Room charge (double occupancy). [17] \medskip

\underline{Previous Answer}: 11110\medskip

\TextField[width = 6 in,multiline, name=90020]{} \medskip

\item Board charge (maximum plan). [18] \medskip

\underline{Previous Answer}: 6610\medskip

\TextField[width = 6 in,multiline, name=90021]{} \medskip

\item Combined room and board charge (answer only if you CANNOT separate room and board charges). [19] \medskip

\TextField[width = 6 in,multiline, name=90022]{} \medskip

\item Please record any comments or additional stupulations on undergraduate room and board [20] \medskip

\underline{Previous Answer}: Charges may vary by program, class year, campus/location, meal plan and room type\medskip

\TextField[width = 6 in,multiline, name=90023]{} \medskip

\item Please provide your institution's undergraduate admission office phone number (include area code) [21] \medskip

\underline{Previous Answer}: 7189902000\medskip

\TextField[width = 6 in,multiline, name=90024]{} \medskip

\item Please provide your institution's undergraduate admission office email address. [22] \medskip

\underline{Previous Answer}: adnhealp@stjohns.edu\medskip

\TextField[width = 6 in,multiline, name=90025]{} \medskip

\item Please provide your institution's undergraduate admission office website URL. [23] \medskip

\underline{Previous Answer}: https://www.stjohns.edu/admission/undergraduate-admission\medskip

\TextField[width = 6 in,multiline, name=90026]{} \medskip

\item Please provide a link to your institution's athletics website. [41] \medskip

\underline{Previous Answer}: https://www.stjohns.edu/athletics\medskip

\TextField[width = 6 in,multiline, name=90103]{} \medskip

\item Please use this space for any comments or additional information on sports. [42] \medskip

\TextField[width = 6 in,multiline, name=90104]{} \medskip

\item Please provide a link to graduate student admission information at your institution [50] \medskip

\underline{Previous Answer}: https://www.stjohns.edu/admission/graduate-admission\medskip

\TextField[width = 6 in,multiline, name=90111]{} \medskip

\item Please provide a link to information about graduate student tuition and fees [51] \medskip

\underline{Previous Answer}: https://www.stjohns.edu/admission/tuition-and-financial-aid/graduatelaw-aid\medskip

\TextField[width = 6 in,multiline, name=90112]{} \medskip

\item Does your institution offer any non-state or non-federal opportunity programs that are unique to your institution? [52] \medskip

\underline{Choices}: Yes; No\medskip

\underline{Previous Answer}: No\medskip

\TextField[width = 6 in,multiline, name=90113]{} \medskip

\item Comments on non-state, non-federal opportunity programs [53] \medskip

\TextField[width = 6 in,multiline, name=90114]{} \medskip

\item Please provide a link at your institution for non-state or non-federal opportunity programs [54a] \medskip

\TextField[width = 6 in,multiline, name=90115]{} \medskip

\item Please provide a contact person at your institution for non-state or non-federal opportunity programs [54b] \medskip

\TextField[width = 6 in,multiline, name=90116]{} \medskip

\item Title of contact person [54c] \medskip

\TextField[width = 6 in,multiline, name=90117]{} \medskip

\item Email of contact person [54d] \medskip

\TextField[width = 6 in,multiline, name=90118]{} \medskip

\item Phone of contact person [54e] \medskip

\TextField[width = 6 in,multiline, name=90119]{} \medskip

\item Non-state, non-federal opportunity program description [55] \medskip

\TextField[width = 6 in,multiline, name=90120]{} \medskip

\item Does your institution offer ROTC opportunities [56] \medskip

\underline{Choices}: Yes; No\medskip

\underline{Previous Answer}: Yes\medskip

\TextField[width = 6 in,multiline, name=90121]{} \medskip

\item Does your institution have a Navy ROTC program, and is it offered on-site or at a neighboring/affiliated institution [57a] \medskip

\underline{Choices}: On-site; Neighboring/affiliated; Neither\medskip

\TextField[width = 6 in,multiline, name=90122]{} \medskip

\item Does your institution have an Army ROTC program, and is it offered on-site or at a neighboring/affiliated institution [57b] \medskip

\underline{Choices}: On-site; Neighboring/affiliated; Neither\medskip

\underline{Previous Answer}: On-site\medskip

\TextField[width = 6 in,multiline, name=90123]{} \medskip

\item Does your institution have an Air Force ROTC program, and is it offered on-site or at a neighboring/affiliated institution [57c] \medskip

\underline{Choices}: On-site; Neighboring/affiliated; Neither\medskip

\TextField[width = 6 in,multiline, name=90124]{} \medskip

\item Describe briefly any special or unique programs or services that you wish to highlight and would be of interest to prospective students and parents. We are also very interested in information about successful retention, student success, and programs for non-tradition students. Please include any relevant links or contact information that CICU can access to gather additional information about these unique programs. [58] \medskip

\TextField[width = 6 in,multiline, name=90125]{} \medskip

\end{enumerate}
\newpage
\end{Form}
\end{document}
